A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-04-15 paper/paper.tex
more writing

\noindent The proof of this theorem relies on a complete census of positively curved combinatorial 3-manifolds completed by Lutz and Sullivan. The census contains 4787 manifolds, with the following topologies represented: the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$, and the cube space $S^3/Q$. The creation of such a census is a highly non-trivial task, for details see \cite{LutzSul}.

@@

\begin{thm}(Unique Extension) If two paths $P_1$ and $P_2$ in $\mathcal{P}$ pass through the same first two simplices of $M$ and have the same length, then $P_1 = P_2$. This result is false if $\mathcal{P}$ is replaced by $\mathcal{P}_1$.
\end{thm}

>>>>

\noindent The proof of this theorem relies on the remarkable work of Lutz, Sullivan and Sulanke in \cite{Lutz07, LutzSul_unpub, sulanke2009isomorphism} who created a complete census of positively curved combinatorial 3-manifolds (see \cite{Lutz_online}.) This census contains 4787 manifolds, with the following topologies represented: the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$, and the cube space $S^3/Q$. Note that all manifolds are either homeomorphic to a 3-sphere or to the quotient space of a 3-sphere under the action of a finite group.

@@

\begin{thm}(Unique Extension) If two minimal paths $P_1$ and $P_2$ in $\mathcal{P}$ pass through the same first two simplices of a positively curved 3-manifold $M$ and $P_1$ and $P_2$ have the same length, then $P_1 = P_2$. This result is false if $\mathcal{P}$ is replaced by $\mathcal{P}_1$.
\end{thm}
